Draft for project

### 2014-12-18 draft_project.tex
Tror jeg skal levere nå...

\begin{theorem}[Strong maximum principle]
\begin{enumerate}[i)]
	Suppose $\Omega$ is connected, and $u\in C^{2,1}(Q_T)\cap C(\overline{Q}_T)$, and $\partial_t + L$ is uniformly parabolic, then:
	\item If
	\begin{equation*}
		\partial_tu + Lu \leq 0, \quad \text{ in } Q_T, 
	\end{equation*}
	and $u$ attains its maximum over $\overline{Q}_T$ at point $(x_0,t_0)\in Q_T$, then
	$u$ is constant on $Q_{t_0}$.

@@

Recalling the divergence form (\ref{divergence_operator}) at the beginning of this section, it will be useful to consider a general parabolic equation of the form
\begin{equation}
\label{lady_parabolic_eq}
	u_t - \sum_{i=1}^d\frac{d}{dx_i}a_i(x,t,u,\nabla u) + a(x,t,u,\nabla u) = 0
\end{equation}
in $Q_T$. In addition we formulate the initial value and boundary as
\begin{equation}
\label{lady_bc}
	u\big|_{\Gamma_T} = \psi\big|_{\Gamma_T}
\end{equation}
for some known function $\psi$.

@@

		\item $u_0$ is in $C^2_c(\Omega)$; $u_0\in C^2(\Omega)$ and has compact support.

		\item $\partial \Omega$ is $C^{2+\beta}$-smooth.

@@

	Considering the first inequality in (\ref{exist_cond3}) we have
	\begin{equation*}
		\sum_{i,j=1}^d \frac{\partial a_i(x,t,u,p)}{\partial p_j} \xi_i \xi_j = \sum_{i=1}^d \Phi'(u)\xi_i^2 =\Phi'(u)\xi^2,
	\end{equation*}
	which is satisfied because of (\ref{uniform_parabGPME}).

@@

Recall our definition of $\Psi$ in (\ref{phi_primitive}) as the primitive of $\Phi$,
and we define the function space $L_\Psi(\Omega) = \{ u\in L^1(\Omega): \Psi(u)\in L^1(\Omega)\}$. This is with the norm
\begin{equation}
||u||_{L_\Psi (\Omega)} = ||u||_{L^1(\Omega)} + ||\Psi(u)||_{L^1(\Omega)}.
\end{equation}
With this in mind we can define energy solutions in the following way:
\begin{mydef}[Energy solution]
We say that $u$ is a \textbf{weak energy solution} if it's a weak solution, $u_0 \in L_\Psi(\Omega)$, and the energy inequality
\begin{equation}
\label{energy_ineq}
\iint_{Q_T} |\nabla \Phi(u)|^2 dxdt + \int_\Omega \Psi(u(x,T))dx \leq \int_\Omega \Psi(u_0)dx + \iint_{Q_T}f\Phi(u)dxdt
\end{equation}
holds.
\end{mydef}
\setcounter{obs}{0}
\begin{obs}
If $f\in L^2(Q_T)$ we can do the same trick on the right hand side as we did in deriving (\ref{spatial_derivative_bound_w_poincare}), to get that $\Phi(u) \in L^2(0,T: H^1_0(\Omega))$.
\end{obs}

@@

We define the approximations of $f$ in a similar manner: Let $\tilde{f}_n = \mathrm{max}\{ \mathrm{min}\{f,n \}, -n\}$, and then define $f_n = \tilde{f}_n * \varphi_{\frac{1}{n}}$.
Notice that by Young's inequality $||f_n||_{L^2(Q_T)} \leq ||\tilde{f}_n||_{L^2(Q_T)} \leq ||f||_{L^2(Q_T)}$.

@@

\begin{lemma}
\label{prop:spatial_boundedness}
With the same assumptions as in Lemma \ref{prop:classical_sols_seq},
the sequences $(w_n)$ and $(\nabla w_n)$ are uniformly bounded in $L^2(Q_T)$. In other words $(w_n)$ is uniformly bounded $L^2(0,T: H^1_0(\Omega))$. Moreover, there is some $K >0$, depending only on $M$ from Lemma \ref{prop:classical_sols_seq} and $\Phi$, so that
\begin{equation}
\label{gradwn_bound_uniform}
||\nabla w_n||_{L^2(Q_T)} \leq K||u_0||_{L^1(\Omega)} + ||f||_{L^2(Q_T)}.
\end{equation}
for all $n$.
\end{lemma}
\begin{proof}
Since $u_n$ are classical solutions, we use (\ref{spatial_derivative_bound_w_poincare}) to get that
	\begin{equation}
	\label{exist_proof_spatial}
	\frac{1}{2}\iint_{Q_T}|\nabla w_n|^2 dxdt + \int_\Omega \Psi_n(u_n(T))dx  \leq \int_\Omega \Psi_n(u_{0,n})dx + C\iint_{Q_T}f_n^2 dxdt
	\end{equation}
	holds for each $n$.

@@

	Now we derive an estimate on the $\Phi_n$-part in terms of $\Phi$ and $u_0$. A crude estimate will be sufficient, and we have
	\begin{align*}
	|\Phi_n(u) - \Phi(u)| &= \left|\frac{u}{n} + \int_\mathbb{R}\left( \Phi(u-y) - \Phi(u) - \Phi(y)\right)\varphi_{\frac{1}{n}}(y)dy \right| \\
	&\leq \frac{|u|}{n} + \underset{y\in [-1/n, 1/n]}{\mathrm{sup}}|\Phi(u-y) - \Phi(u)| + \mathrm{max}\{|\Phi(-1/n)|, |\Phi(1/n)|\} \\
	&\leq |u| + \underset{y\in [-1, 1]}{\mathrm{sup}}|\Phi(u-y) - \Phi(u)| +\mathrm{max}\{|\Phi(-1)|, |\Phi(1)|\},
	\end{align*}
	where we have used that $\mathrm{supp}(\varphi_{\frac{1}{n}})\subset [-1/n, 1/n]$ as well as that $\Phi$ is monotone. This, when considering $u_{0,n}$, we have
	\begin{align*}
	|\Phi_n(u_{0,n})| &\leq |\Phi(u_{0,n})| + |u_{0,n}| + \underset{y\in [-1, 1]}{\mathrm{sup}}|\Phi(u_{0,n}-y) - \Phi(u_{0,n})| +\mathrm{max}\{|\Phi(-1)|, |\Phi(1)|\} \\
	& \leq \underset{|s| \leq ||u_0||_\infty}{\mathrm{sup}}|\Phi(s)| + ||u_0||_{\infty}\\
	& + \underset{\underset{y\in[-1/n,1/n]}{|s| \leq ||u_0||_{\infty}}}{\mathrm{sup}}|\Phi(s-y) - \Phi(s)| + \mathrm{max}\{|\Phi(-1)|, |\Phi(1)|\} \\
	&=: K < \infty.
	\end{align*}
	In the last step we also made repeated use of $|u_{0,n}| \leq ||u_0||_\infty$.
	All terms are bounded since $u_0$ is bounded. When also using that $||u_{0,n}||_{L^1(\Omega)} \leq ||u_0||_{L^1(\Omega)}$ we finally get the estimate
	\begin{align*}
	\int_\Omega \Psi_n(u_{0,n})dx &\leq K ||u_{0,n}||_{L^1(\Omega)} \\
	&\leq K ||u_0||_{L^1(\Omega)}
	\end{align*}
	which is finite from $u_0 \in L^1(\Omega)$. Most importantly, this shows that the left hand side of (\ref{exist_proof_spatial}) is bounded independently of $n$, which immediately implies that $\nabla w_n$ is a bounded sequence in $L^2(Q_T)$. Notice also that from the Poincaré inequality,
	\begin{equation*}
	\iint_{Q_T}w_n^2 dxdt \leq C\iint_{Q_T} |\nabla w_n|^2dxdt,	
	\end{equation*}
	$w_n$ is also uniformly bounded in $L^2(Q_T)$.
\end{proof}

@@

We can get a similar convergence result for $\nabla w_{n_j}$:
\begin{lemma}
\label{prop:gradw_weak_convergence}
With the same assumptions as in proposition \ref{prop:classical_sols_seq},
$\nabla w_{n_j}$ converges weakly to $\nabla w$ in $L^2(Q_T)$.
\end{lemma}
\begin{proof}
First off we note that $\nabla w_{n_j}$ converges to $\nabla w$ in the distributional sense. Indeed, the distributional gradient of $w_{n_j}$ is defined by
	\begin{equation}
	\iint_{Q_T}\nabla w_{n_j}\cdot \psi dxdt = -\iint_{Q_T} w_{n_j} \nabla \cdot \psi dxdt ,
	\end{equation}
	which is to hold for every $\psi \in C^\infty_c(Q_T)$. Since $w_{n_j}$ converges weakly to $w$
	\begin{align*}
	\iint_{Q_T}\nabla w_{n_j} \cdot \psi dxdt &= -\iint_{Q_T} w_{n_j} \nabla \cdot \psi dxdt \\
	&\to -\iint_{Q_T} w \nabla \cdot \psi dxdt \\
	&= \iint_{Q_T} \nabla w \cdot \psi dxdt,
	\end{align*}
	where the last inequality is by definition of the distributional derivative. From this we deduce that $\nabla w_{n_j}$ converges to $\nabla w$ in the distributional sense.

@@

\begin{description}
	\item[Convergence of $u_{n_j}$:] Both $\Phi$ and its approximations $\Phi_n$ all admit a continuous inverse (cf. appendix \ref{app:Phi}), and so
	\begin{equation*}
	u_{n_j} = \Phi_{n_j}^{-1}(w_{n_j}).
	\end{equation*}
	We now simply have by the triangle inequality
	\begin{align*}
	|u_{n_j} - \Phi^{-1}(w)| &= |\Phi_{n_j}^{-1}(w_{n_j}) - \Phi^{-1}(w)| \\
		&\leq |\Phi_{n_j}^{-1}(w_{n_j}) - \Phi^{-1}(w_{n_j})| + |\Phi^{-1}(w_{n_j}) - \Phi^{-1}(w)|.
	\end{align*}
	 We have that $w_{n_j}$ is a bounded sequence, seeing as $u_{n_j}$ is bounded. Hence we can use proposition \ref{prop:inverse_uniform} to make the first term in the above inequality arbitrarily small. The second term is controlled by the almost everywhere convergence of $w_{n_j}$ to $w$ and the continuity of $\Phi^{-1}$. That means that
	 \begin{equation*}
	 u_{n_j} \to u = \Phi^{-1}(w)
	 \end{equation*}
	 almost everywhere. We immediately see that $\Phi(u) = w$.

@@

	\item[$u \in L^\infty(0,T: L_\Psi(\Omega)$:]
	For any $t \in [0,T]$ we have by Fatou's Lemma \citep[p. 162]{weiss1999course} that 
	\begin{equation*}
	||u(t)||_{L^1(\Omega)} \leq \liminf_{n \to \infty} ||u_n(t)||_{L^1(\Omega)}.
	\end{equation*}
	Here we use Corollary \ref{cor:l1-contractivity_classical} with $\hat{u}=0$ as the solution to zero loading and initial data to get that
	\begin{align}
	||u(t)||_{L^1(\Omega)} &\leq \liminf_{n \to \infty} \left( ||u_{0,n}||_{L^1(\Omega)} + ||f_n||_{L^1(Q_T)}\right) \nonumber \\
	&= ||u_0||_{L^1(\Omega)} + ||f||_{L^1(Q_T)},	
	\end{align}
	implying that $u \in L^\infty(0,T: L^1(\Omega))$.

	We do similarly for $\Psi(u(t))$, but first we need to show that $\Psi_n(u_n)$ converges almost everwhere to $\Psi(u)$. We use the triangle inequality as
	\begin{equation}
	|\Psi_n(u_n) - \Psi(u)| \leq |\Psi_n(u_n) - \Psi(u_n)| + |\Psi(u_n) + \Psi(u)|.
	\end{equation}
	Because $|u_n| \leq M$ we use that $\Psi_n$ converges uniformly on compact sets (see proposition \ref{prop:Psi_uniform_convergence}) to control the first term. The second term is controlled by the almost everywhere convergence of $u_n$ to $u$ and the continuity of $\Psi$.

	Then, by Fatou's Lemma
	\begin{equation*}
	\int_\Omega \Psi(u(t))dx \leq \liminf_{n \to \infty} \int_\Omega \Psi_n(u_n(t))dx,
	\end{equation*}
	since $\Psi_n$ is nonnegative. Using Corollary \ref{cor:spatial_bound_w_poincare} we get
	\begin{align*}
	\int_\Omega \Psi(u(t))dx &\leq \liminf_{n \to \infty} \left( \int_\Omega \Psi_n(u_{0,n})dx + C\iint_{Q_T}f_n^2 dxdt \right)\nonumber \\
	&= \int_\Omega \Psi(u_0)dx + \iint_{Q_T} f^2dxdt, 
	\end{align*}
	and so we have that $u \in L^\infty(0,T: L_\Psi(\Omega))$.

@@

	We have from before that $u\in L^2(Q_T)$ as well as $\Phi(u) \in L^2(0,T: H^1(\Omega))$, so the solution is unique. In addition it is worth noticing that any accumulation point of the sequence of classical solutions is a weak solution, and so the uniqueness in theorem \ref{thm:uniqueness} precludes any other accumulation point than $u$. I.e. the whole sequence $(u_n)$ converges to $u$.

@@

\subsubsection{No longer $C^{2,\alpha}$ boundary}
Following suit from the previous section, we'll now aim to prove Lemma \ref{lem:weak_existence_part2} without the assumption that $\partial \Omega$ is $C^{2,\alpha}$, of course, this is usually the case in applications, where the domain can have corners and such, making the boundary not sufficiently smooth to satisfy the assumptions in theorem \ref{thm:classical_existence} to provide a classical solution. The strategy for proving existence now will be to get a sequence of weak solution on smaller subdomains that will eventually converge to all of $Q_T$.

@@

\begin{equation*}
\iint_{Q_T} |\nabla w_n|^2dxdt + \int_\Omega \Psi(u_n(T)) = \iint_{Q_n}|\nabla w_n|^2dxdt + \int_{K_n} \Psi(u_n(T))dx.
\end{equation*}
For each $n$, $u_n$ is a weak energy solution in $Q_n$ and as satisfies \ref{energy_ineq}, giving
\begin{align}
\label{step_spatial_bound_z_nonsmooth_boundary}
\iint_{Q_T} |\nabla w_n|^2dxdt + \int_\Omega \Psi(u_n(T)) &\leq \int_{K_n}\Psi(u_{0,n})dx + \iint_{Q_n}f_n w_n dxdt \nonumber \\
&= \int_\Omega \Psi(u_{0,n})dx + \iint_{Q_T} f_n w_n dxdt \nonumber\\
& \leq \int_\Omega \Psi(u_0)dx + \iint_{Q_T} f_n w_n dxdt,
\end{align}
where we've also made use of that $|u_{0,n}| \leq |u_0|$, as well as that $w_n$ and $u_{0,n}$ vanish outside of $Q_n$ and $K_n$ respectively.
$w_n$ is in $L^2(0,T:H_0^1(\Omega))$ for each $n$, so use of the inequality $ab \leq \frac{a^2}{4c} + cb^2$ on the last term on the right hand side yields
\begin{equation*}
\iint_{Q_T} f_n w_n dxdt \leq \frac{1}{4c}\iint_{Q_T}f_n^2dxdt + c\iint_{Q_T} w_n^2 dxdt.
\end{equation*}

@@

By Lemma \ref{prop:z_t_estimate} we can use the estimate (\ref{z_t_estimate}) as
\begin{equation}
\label{z_n_bounded_in_H1_start}
\iint_{Q_T^\tau} |\partial_t z_n|^2 dxdt \leq \frac{||\partial_t \zeta||_\infty}{2}\left( K||u_{0,n}||_{L^1(K_n)} + ||f_n||_{L^2(Q_n)}\right) + \iint_{Q_n}|\partial_t (f_n \zeta ) w_n| dxdt,
\end{equation}
where $\zeta = \zeta(t)$ is a smooth cutoff function from Lemma \ref{prop:z_t_estimate}, which has a bounded derivative.

@@

\subsubsection{Removing the assumptions on $f$ and $u_0$}
We've finally arrived at the last section, where we'll prove theorem \ref{thm:weak_existence} without the assumption \ref{ass:f_ft_u_0_bounded}, which have proved so very useful for us up to this point. Let's just get to it then.

@@

\item[$\nabla \Phi(u_n)$ converges weakly to $\nabla \Phi(u)$:]
The proof of this assertion is done, as in the proof of proposition \ref{prop:gradw_weak_convergence}, by noticing from the weak convergence of $\Phi(u_n)$ we can deduce that $\nabla \Phi(u_n)$ converges to $\nabla \Phi(u)$ in the distributional sense. In addition $\nabla \Phi(u_n)$ is a bounded sequence in $L^2(Q_T)$, and so every subsequence has a weakly convergent subsequence. Arguing as before, the limit point is always $\nabla \Phi(u)$, and so $\nabla \Phi(u_n)$ converges weakly to $\nabla \Phi(u)$.

\item[$u$ is a weak solution:]
With the various convergences shown above or given by assumption, showing that $u$ is a weak solution and satisfies the energy inequality (\ref{energy_ineq}) is done identically as in the proof of lemma \ref{lem:existence_part1}. The same is true for showing that $u$ satisfies the energy inequality (\ref{energy_ineq}).
\end{description}
\end{proof}

@@

\begin{proposition}
$\Phi_n^{-1}$ converges pointwise to $\Phi^{-1}$.
\end{proposition}

>>>>

\begin{theorem}[Strong maximum principle]
\begin{enumerate}[i)]
	Suppose $\Omega$ is connected, and $u\in C^2_1(Q_T)\cap C(\overline{Q}_T)$, and $\partial_t + L$ is uniformly parabolic, then:
	\item If
	\begin{equation*}
		\partial_tu + Lu \leq 0, \quad \text{ in } Q_T, 
	\end{equation*}
	and $u$ attains its maximum over $\overline{Q}_T$ at point $(x_0,t_0)\in Q_T$, then
	$u$ is constant on $Q_{t_0}$.

@@

Recalling the divergence form (\ref{divergence_operator}) at the beginning of this section, it will be useful to consider a general parabolic equation of the form
\begin{equation}
\label{lady_parabolic_eq}
	u_t - \sum_{i=1}^d\frac{\partial}{\partial x_i}a_i(x,t,u,\nabla u) + a(x,t,u,\nabla u) = 0
\end{equation}
in $Q_T$. In addition we formulate the initial value and boundary as
\begin{equation}
\label{lady_bc}
	u\big|_{\Gamma_T} = \psi\big|_{\Gamma_T}
\end{equation}
for some known function $\psi$.

@@

		\item $u_0\in C^2(\Omega)$, and $u_0$, $\nabla u_0$ and $\Delta u_0$ vanish at the boundary.

		\item $\partial \Omega$ is $C^{2,\beta}$-smooth.

@@

	Considering the first inequality in (\ref{exist_cond3}) we have
	\begin{equation*}
		\sum_{i,j=1}^d \frac{\partial a_i(x,t,u,p)}{\partial p_j} \xi_i \xi_j = \sum_{i=1}^d \Phi'(u)\xi_i^2 =\Phi'(u)|\xi|^2,
	\end{equation*}
	which is satisfied because of (\ref{uniform_parabGPME}).

@@

Recall our definition of $\Psi$ in (\ref{phi_primitive}) as the primitive of $\Phi$,
and we define the function space $L_\Psi(\Omega) = \{ u\in L^1(\Omega): \Psi(u)\in L^1(\Omega)\}$. This is with the norm
\begin{equation}
||u||_{L_\Psi (\Omega)} = ||u||_{L^1(\Omega)} + ||\Psi(u)||_{L^1(\Omega)}.
\end{equation}
With this in mind we can define energy solutions in the following way:
\begin{mydef}[Energy solution]
We say that $u$ is a \textbf{weak energy solution} if it's a weak solution, $u_0 \in L_\Psi(\Omega)$, and the energy inequality
\begin{equation}
\label{energy_ineq}
\iint_{Q_T} |\nabla \Phi(u)|^2 dxdt + \int_\Omega \Psi(u(x,T))dx \leq \int_\Omega \Psi(u_0)dx + \iint_{Q_T}f\Phi(u)dxdt
\end{equation}
holds.
\end{mydef}
\setcounter{obs}{0}
\begin{obs}
If $f\in L^2(Q_T)$ we can do the same trick on the right hand side as we did in deriving (\ref{spatial_derivative_bound_w_poaincare}), to get that $\Phi(u) \in L^2(0,T: H^1_0(\Omega))$.
\end{obs}

@@

We define the approximations of $f$ in a similar manner: Let $\tilde{f}_n = \mathrm{max}\{ \mathrm{min}\{f,n \}, -n\}$, and then define $f_n = \tilde{f}_n * \varphi_{\frac{1}{n}}$.
Notice that by Young's inequality $||f_n||_{L^2(Q_T)} \leq ||\tilde{f}_n||_{L^2(Q_T)} \leq ||f||_{L^2(Q_T)}$. Because of $\partial_t (\tilde{f}_n* \varphi_{\frac{1}{n}}) = (\partial_t \tilde{f}_n) *\varphi_{\frac{1}{n}}$, we also have that $||\partial_t f_n||_\infty \leq ||\partial_t f||_\infty$. This is true for any derivative of $f$ that exists, but it's only the time derivative estimate here that will become useful to us.

@@

\begin{lemma}
\label{prop:spatial_boundedness}
With the same assumptions as in Lemma \ref{prop:classical_sols_seq},
the sequences $(w_n)$ and $(\nabla w_n)$ are uniformly bounded in $L^2(Q_T)$. In other words $(w_n)$ is uniformly bounded $L^2(0,T: H^1_0(\Omega))$. Moreover, there are constants $B_1, B_2 >0$ depending only on $M$ from Lemma \ref{prop:classical_sols_seq} and $\Phi$, so that
\begin{equation}
\label{gradwn_bound_uniform}
||\nabla w_n||_{L^2(Q_T)} \leq B_1||u_0||_{L^1(\Omega)} + B_2||f||_{L^2(Q_T)}.
\end{equation}
for all $n$.
\end{lemma}
\begin{proof}
Since $u_n$ are classical solutions, we use (\ref{spatial_derivative_bound_w_poaincare}) to get that
	\begin{equation}
	\label{exist_proof_spatial}
	\frac{1}{2}\iint_{Q_T}|\nabla w_n|^2 dxdt + \int_\Omega \Psi_n(u_n(T))dx  \leq \int_\Omega \Psi_n(u_{0,n})dx + C\iint_{Q_T}f_n^2 dxdt
	\end{equation}
	holds for each $n$.

@@

	Now we derive an estimate on the $\Phi_n$-part in terms of $\Phi$ and $u_0$. A crude estimate will be sufficient, and we have
	\begin{align*}
	|\Phi_n(u) - \Phi(u)| &= \left|\frac{u}{n} + \int_\mathbb{R}\left( \Phi(u-y) - \Phi(u) - \Phi(y)\right)\varphi_{\frac{1}{n}}(y)dy \right| \\
	&\leq \frac{|u|}{n} + \underset{y\in [-1/n, 1/n]}{\mathrm{sup}}|\Phi(u-y) - \Phi(u)| + \mathrm{max}\{|\Phi(-1/n)|, |\Phi(1/n)|\} \\
	&\leq |u| + \underset{y\in [-1, 1]}{\mathrm{sup}}|\Phi(u-y) - \Phi(u)| +\mathrm{max}\{|\Phi(-1)|, |\Phi(1)|\},
	\end{align*}
	where we have used that $\mathrm{supp}(\varphi_{\frac{1}{n}})\subset [-1/n, 1/n]$ as well as that $\Phi$ is monotone. This, when considering $u_{0,n}$, we have
	\begin{align*}
	|\Phi_n(u_{0,n})| &\leq |\Phi(u_{0,n})| + |u_{0,n}| + \underset{y\in [-1, 1]}{\mathrm{sup}}|\Phi(u_{0,n}-y) - \Phi(u_{0,n})| +\mathrm{max}\{|\Phi(-1)|, |\Phi(1)|\} \\
	& \leq \underset{|s| \leq ||u_0||_\infty}{\mathrm{sup}}|\Phi(s)| + ||u_0||_{\infty}\\
	& + \underset{\underset{y\in[-1/n,1/n]}{|s| \leq ||u_0||_{\infty}}}{\mathrm{sup}}|\Phi(s-y) - \Phi(s)| + \mathrm{max}\{|\Phi(-1)|, |\Phi(1)|\} \\
	&=: \frac{B_1}{2} < \infty.
	\end{align*}
	In the last step we also made repeated use of $|u_{0,n}| \leq ||u_0||_\infty$.
	All terms are bounded since $u_0$ is bounded. When also using that $||u_{0,n}||_{L^1(\Omega)} \leq ||u_0||_{L^1(\Omega)}$ we finally get the estimate
	\begin{align*}
	\int_\Omega \Psi_n(u_{0,n})dx &\leq \frac{B_1}{2} ||u_{0,n}||_{L^1(\Omega)} \\
	&\leq \frac{B_1}{2} ||u_0||_{L^1(\Omega)}
	\end{align*}
	which is finite from $u_0 \in L^1(\Omega)$. Most importantly, this shows that the left hand side of (\ref{exist_proof_spatial}) is bounded independently of $n$, which immediately implies that $\nabla w_n$ is a bounded sequence in $L^2(Q_T)$. Notice also that from the Poincaré inequality,
	\begin{equation*}
	\iint_{Q_T}w_n^2 dxdt \leq C\iint_{Q_T} |\nabla w_n|^2dxdt,	
	\end{equation*}
	$w_n$ is also uniformly bounded in $L^2(Q_T)$. Lastly, setting $B_2 = 2C$ and multplying (\ref{exist_proof_spatial}) by $2$ we get
	\begin{equation}
	\iint_{Q_T} |\nabla w_n|^2 dxdt \leq B_1 ||u_0||_{L^1(\Omega)} + B_2 ||f||_{L^2(Q_T)}.
	\end{equation}
\end{proof}

@@

We can get a similar convergence result for $\nabla w_{n_j}$:
\begin{lemma}
\label{prop:gradw_weak_convergence}
With the same assumptions as in Lemma \ref{prop:classical_sols_seq},
$\nabla w_{n_j}$ converges weakly to $\nabla w$ in $L^2(Q_T)$.
\end{lemma}
\begin{proof}
First off we note that $\nabla w_{n_j}$ converges to $\nabla w$ in the distributional sense. Indeed, the distributional gradient of $w_{n_j}$ is defined by
	\begin{equation}
	\iint_{Q_T}\nabla w_{n_j}\cdot \psi dxdt = -\iint_{Q_T} w_{n_j} \nabla \cdot \psi dxdt ,
	\end{equation}
	which is to hold for every $\psi \in C^\infty_c(Q_T)$. Since $w_{n_j}$ converges weakly to $w$
	\begin{align*}
	\iint_{Q_T}\nabla w_{n_j} \cdot \psi dxdt &= -\iint_{Q_T} w_{n_j} \nabla \cdot \psi dxdt \\
	&\to -\iint_{Q_T} w \nabla \cdot \psi dxdt \\
	&= \iint_{Q_T} \nabla w \cdot \psi dxdt,
	\end{align*}
	where the last inequality is by definition of the distributional derivative. From this we deduce that $\nabla w_{n_j}$ converges to $\nabla w$ in the distributional sense.

@@

\begin{description}
	\item[Convergence of $u_{n_j}$:] Both $\Phi$ and its approximations $\Phi_n$ all admit a continuous inverse (cf. appendix \ref{app:Phi}), and so
	\begin{equation*}
	u_{n_j} = \Phi_{n_j}^{-1}(w_{n_j}).
	\end{equation*}
	We now simply have by the triangle inequality
	\begin{align*}
	|u_{n_j} - \Phi^{-1}(w)| &= |\Phi_{n_j}^{-1}(w_{n_j}) - \Phi^{-1}(w)| \\
		&\leq |\Phi_{n_j}^{-1}(w_{n_j}) - \Phi^{-1}(w_{n_j})| + |\Phi^{-1}(w_{n_j}) - \Phi^{-1}(w)|.
	\end{align*}
	 We have that $w_{n_j}$ is a bounded sequence, seeing as $u_{n_j}$ is bounded. Hence we can use Lemma \ref{prop:inverse_uniform} to make the first term in the above inequality arbitrarily small. The second term is controlled by the almost everywhere convergence of $w_{n_j}$ to $w$ and the continuity of $\Phi^{-1}$. That means that
	 \begin{equation*}
	 u_{n_j} \to u = \Phi^{-1}(w)
	 \end{equation*}
	 almost everywhere. We immediately see that $\Phi(u) = w$.

@@

	\item[$u \in L^\infty(0,T: L_\Psi(\Omega)$:]
	For almost every $t \in [0,T]$ we have by Fatou's Lemma \citep[p. 162]{weiss1999course} that since $|u_{n_j}(t)|$ converges almost everywhere to $|u(t)|$ and are nonnegative, then
	\begin{equation*}
	||u(t)||_{L^1(\Omega)} \leq \liminf_{j \to \infty} ||u_{n_j}(t)||_{L^1(\Omega)}.
	\end{equation*}
	Here we use Corollary \ref{cor:l1-contractivity_classical} with $\hat{u}=0$ as the solution to zero loading and initial data to get that
	\begin{align}
	||u(t)||_{L^1(\Omega)} &\leq \liminf_{j \to \infty} \left( ||u_{0,n_j}||_{L^1(\Omega)} + ||f_{n_j}||_{L^1(Q_T)}\right) \nonumber \\
	&= ||u_0||_{L^1(\Omega)} + ||f||_{L^1(Q_T)},	
	\end{align}
	implying that $u \in L^\infty(0,T: L^1(\Omega))$.

	We do similarly for $\Psi(u(t))$, but first we need to show that $\Psi_n(u_n)$ converges almost everwhere to $\Psi(u)$. We use the triangle inequality as
	\begin{equation}
	|\Psi_{n_j}(u_{n_j}) - \Psi(u)| \leq |\Psi_{n_j}(u_{n_j}) - \Psi(u_{n_j})| + |\Psi(u_{n_j}) + \Psi(u)|.
	\end{equation}
	Because $|u_n| \leq M$ we use that $\Psi_n$ converges uniformly on compact sets (see Lemma \ref{prop:Psi_uniform_convergence}) to control the first term. The second term is controlled by the almost everywhere convergence of $u_{n_j}$ to $u$ and the continuity of $\Psi$.

	Then, by Fatou's Lemma
	\begin{equation*}
	\int_\Omega \Psi(u(t))dx \leq \liminf_{n \to \infty} \int_\Omega \Psi_n(u_n(t))dx,
	\end{equation*}
	since $\Psi_n$ is nonnegative. Using Corollary \ref{cor:spatial_bound_w_poincare} we get
	\begin{align*}
	\int_\Omega \Psi(u(t))dx &\leq \liminf_{j \to \infty} \left( \int_\Omega \Psi_{n_j}(u_{0,n_j})dx + C\iint_{Q_T}f_{n_j}^2 dxdt \right)\nonumber \\
	&= \int_\Omega \Psi(u_0)dx + \iint_{Q_T} f^2dxdt, 
	\end{align*}
	and so we have that $u \in L^\infty(0,T: L_\Psi(\Omega))$.

@@

	We have from before that $u\in L^2(Q_T)$ as well as $\Phi(u) \in L^2(0,T: H^1(\Omega))$, so the solution is unique. In addition it is worth noticing that any accumulation point of the sequence of classical solutions is a weak solution, and so the uniqueness in Theorem \ref{thm:uniqueness} precludes any other accumulation point than $u$. I.e. the whole sequence $(u_n)$ converges to $u$.

@@

\subsubsection{No longer $C^{2,\alpha}$ boundary}
Following suit from the previous section, we'll now aim to prove Lemma \ref{lem:weak_existence_part2} without the assumption that $\partial \Omega$ is $C^{2,\alpha}$, of course, this is usually the case in applications, where the domain can have corners and such, making the boundary not sufficiently smooth to satisfy the assumptions in Theorem \ref{thm:classical_existence} to provide a classical solution. The strategy for proving existence now will be to get a sequence of weak solution on smaller subdomains that will eventually converge to all of $Q_T$.

@@

\begin{equation*}
\iint_{Q_T} |\nabla w_n|^2dxdt + \int_\Omega \Psi(u_n(T)) = \iint_{Q_n}|\nabla w_n|^2dxdt + \int_{K_n} \Psi(u_n(T))dx.
\end{equation*}
For each $n$, $u_n$ is a weak energy solution in $Q_n$ and as satisfies (\ref{energy_ineq}), giving
\begin{align}
\label{step_spatial_bound_z_nonsmooth_boundary}
\iint_{Q_T} |\nabla w_n|^2dxdt + \int_\Omega \Psi(u_n(T)) &\leq \int_{K_n}\Psi(u_{0,n})dx + \iint_{Q_n}f_n w_n dxdt \nonumber \\
&= \int_\Omega \Psi(u_{0,n})dx + \iint_{Q_T} f_n w_n dxdt \nonumber\\
& \leq \int_\Omega \Psi(u_0)dx + \iint_{Q_T} f_n w_n dxdt,
\end{align}
where we've also made use of that $|u_{0,n}| \leq |u_0|$, as well as that $w_n$ and $u_{0,n}$ vanish outside of $Q_n$ and $K_n$ respectively.
$w_n$ is in $L^2(0,T:H_0^1(\Omega))$ for each $n$, so use of the inequality $ab \leq \frac{a^2}{4c} + cb^2$ on the last term on the right hand side yields
\begin{equation*}
\iint_{Q_T} f_n w_n dxdt \leq \frac{1}{4c}\iint_{Q_T}f_n^2dxdt + c\iint_{Q_T} w_n^2 dxdt.
\end{equation*}

@@

By Lemma \ref{prop:z_t_estimate} we can use the estimate (\ref{z_t_estimate}) as
\begin{equation}
\label{z_n_bounded_in_H1_start}
\iint_{Q_T^\tau} |\partial_t z_n|^2 dxdt \leq \frac{||\partial_t \zeta||_\infty}{2}\left( B_1||u_{0,n}||_{L^1(K_n)} + B_2||f_n||_{L^2(Q_n)}\right) + \iint_{Q_n}|\partial_t (f_n \zeta ) w_n| dxdt,
\end{equation}
where $\zeta = \zeta(t)$ is a smooth cutoff function from Lemma \ref{prop:z_t_estimate}, which has a bounded derivative.

@@

\subsubsection{Removing the assumptions on $f$ and $u_0$}
We've finally arrived at the last section, where we'll prove Theorem \ref{thm:weak_existence} without the assumption \ref{ass:f_ft_u_0_bounded}, which have proved so very useful for us up to this point. Let's just get to it then.

@@

\item[$\nabla \Phi(u_n)$ converges weakly to $\nabla \Phi(u)$:]
The proof of this assertion is done, as in the proof of Lemma \ref{prop:gradw_weak_convergence}, by noticing from the weak convergence of $\Phi(u_n)$ we can deduce that $\nabla \Phi(u_n)$ converges to $\nabla \Phi(u)$ in the distributional sense. In addition $\nabla \Phi(u_n)$ is a bounded sequence in $L^2(Q_T)$, and so every subsequence has a weakly convergent subsequence. Arguing as before, the limit point is always $\nabla \Phi(u)$, and so $\nabla \Phi(u_n)$ converges weakly to $\nabla \Phi(u)$.

\item[$u$ is a weak solution:]
With the various convergences shown above or given by assumption, showing that $u$ is a weak solution and satisfies the energy inequality (\ref{energy_ineq}) is done identically as in the proof of Lemma \ref{lem:existence_part1}. The same is true for showing that $u$ satisfies the energy inequality (\ref{energy_ineq}).
\end{description}
\end{proof}

@@

\begin{lemma}
With the same assumptions as Lemma \ref{lem:Phi_inv_cont} $\Phi_n^{-1}$ converges pointwise to $\Phi^{-1}$.
\end{lemma}
